Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-05-12 paper2_JNLS/paper.tex
NM

The momentum and energy defined in \eqref{MomEn} remain invariants of TKdV, with the same normalized values $\Mo[\uL] = 0$ and $\En[\uL] = 1$. Note that Parseval's identity implies
\begin{equation}
\En[\uL] = 2 \pi \sum_{k=1}^{\Lambda} \abs{\uhat_k}^2 = 1
\end{equation}
% The above agrees with the first line on top of p. 4 in Majda and Qi J Stat Phys 2019.
Thus, the dynamics of interest are confined to the unit hypersphere, $\En = 1$ in $\CC^{\Lambda}$.
In summary, the TKdV system possesses three important invariants: momentum, energy, and Hamiltonian. The untruncated KdV equation possesses an infinite sequence of additional invariants \cite{lax1975periodic, whitham2011linear}, but their truncated counterparts are not generally invariants of TKdV.

>>>>

The momentum and energy defined in \eqref{MomEn} remain invariants of TKdV, with the same normalized values $\Mo[\uL] = 0$ and $\En[\uL] = 1$. Note that Parseval's identity implies
\begin{equation}
\En[\uL] = 2 \pi \sum_{k=1}^{\Lambda} \abs{\uhat_k}^2 = 1
\end{equation}
Thus, the dynamics of interest are confined to the unit hypersphere, $\En = 1$ in $\CC^{\Lambda}$.
%In summary, the TKdV system possesses three important invariants: momentum, energy, and Hamiltonian.

\new{We comment on some important differences between the KdV and TKdV dynamical systems. In addition to momentum, energy, and Hamiltonian, the KdV system possesses in infinite sequence of invariants, which is, of course, associated with the fact that KdV is a completely integrable system. However, the analogues of these quantities are {\em not} generally invariants of the truncated system. The only known invariants of TKdV are the three mentioned already: momentum, energy, and Hamiltonian. Hence, while KdV is a completely integrable system whose long-time dynamics are governed by soliton interactions, this same behavior should not be expected for TKdV. Instead of breaking into a finite number of solitons, TKdV dynamics become chaotic in long time and have been numerically observed to satisfy weak ergodicity (though no proof is available) \cite{bajars2013weakly}. In this way, the theory developed herein differs from, and could likely complement, recent advances in the field of integrable turbulence \cite{zakharov2009turbulence, randoux2014intermittency, costa2014soliton, randoux2016nonlinear}, where  integrability is exploited to uncover statistical characteristics of the system of interest. 
We remind the reader that KdV is asymptotically valid for large spatial scales and hence truncating the small scales does not alter the order of approximation made. In this sense, KdV and TKdV should be regarded as being on equal footing as far as physical realism. Where differences exist in long-time dynamics, it is unclear {\em a priori} which model, if either, more closely resembles reality.}
